An algorithm for finding the global extremum of a partially defined function\thanks{This work was supported by the Russian Science Foundation, project No. 21-11-00204.}

### 2023-08-27 2023/MMST/samplepaper.tex
one more reference

Note that the use of complex mathematical models is natural in the optimization of complex real world objects that, as a consequence, increases the computation costs for searching the optimum Essentially. In last decades, the experts in the fields of optimization and parallel computations have proposed many methods for reducing the computation costs an speed-up of the algorithms related to solving the appearing optimization problems \cite{Kvasov2013}  as well as to the numerical analysis of the original models \cite{Duwe2020}.

>>>>

Note that the use of complex mathematical models is natural in the optimization of complex real world objects that, as a consequence, increases the computation costs for searching the optimum Essentially. In last decades, the experts in the fields of optimization and parallel computations have proposed many methods for reducing the computation costs an speed-up of the algorithms related to solving the appearing optimization problems \cite{Kvasov2013}  as well as to the numerical analysis of the original models \cite{Dongarra2022,Duwe2020}.
